Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-11-27 ICLR25/proofsb.tex
appendix

We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
Further, we tested with the SR and FSB heuristics \cite{BaB}, that chooses nodes to branch on for BaB (Branch and Bound). When used instead to open nodes for pMILP, SR and FSB result in particularly low accuracy:
even though SR, FSB and \cite{DivideAndSlide} heuristic are all choosing ReLUs based on sensitivity of the target neuron $z$, SR and FSB are worse than \cite{DivideAndSlide} which only opens neurons one layer before, and far away from Utility. Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite situation. This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-8}
		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 & 1.7182 & \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& 1.6803 & \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& 1.6475 & \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & 1.6174 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & 1.5788 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& 1.5413 & \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & 1.4972 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& 1.4514 & \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs SR vs FSB vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

>>>>

We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
Further, we tested with the SR and FSB heuristics \cite{BaB}, that chooses nodes to branch on for BaB (Branch and Bound). When used instead to open nodes for pMILP, SR and FSB result in particularly low accuracy:
even though SR, FSB and \cite{DivideAndSlide} heuristic are all choosing ReLUs based on sensitivity of the target neuron $z$, SR and FSB are worse than \cite{DivideAndSlide} which only opens neurons one layer before (except when all ReLUs of the previous layers are open), and far worse than Utility. Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite. This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-8}
		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729& 1.7133 & 1.7149 & \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6674& 1.6714 & \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& 1.6230& 1.6251 & \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 &1.5764 & 1.5812 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 &1.5322 & 1.5388 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 &  1.4914& 1.4982 & \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4481 & 1.4600 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4070& 1.4187 & \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs SR vs FSB vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

	\begin{figure}[h!]
		\centering
		\vspace*{-0.3cm}
		\includegraphics[height=9cm]{New Plot for table 3}.
		\vspace*{-0.4cm}
		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
		\label{fig_table3_new}
	\end{figure}
